\blue{...Numerical investigation of viscous flow instabilities through heterogeneous porous media using adaptive and unstructured meshes under different mobility scenarios...}

### 2017-07-06 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

%%%%%%%%%%%%%
\subsection{Comparison of fixed and adaptive mesh under heterogeneous domain schemes and the same mobility ratio.}\label{section:results_hete_fix_adapt}    
\medskip

>>>>

%%%%%%%%%%%%%
\subsection{Capturing Flow Dynamics and Fingering Growth with Adaptive Mesh Resolution}\label{section:results_hete_fix_adapt}    
%\subsection{Comparison of fixed and adaptive mesh under heterogeneous domain schemes and the same mobility ratio.}
In most numerical simulations involving geofluid dynamics, local geometric constraints (\eg faults, fractures etc) and spatial multi-scale variability of flow properties are often ignored as the underlying computational mesh grid is too coarse to reliably represent any of these features. Self-adaptive mesh refinement methods have been extensively used by the computational geofluid dynamic community to help capturing detailed flow dynamics, compositional non-equilibrium fluid displacement and solid-fluid interactions \citep[\ie two-way solid-fluid coupling][]{pluszny_2007,pietro_2014,su_2016,melnikova_2016}. In such methods, the mesh grid is continuously modified (\ie adjustments of the number and distribution of the degrees of freedom to reduce solution error) as the simulation evolves in time and space focusing resolution where is necessary.
